\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics

### 2018-12-13 Documents/Euler/Astronum_2018/ms_endeve.tex
Addressing reviewing reviewer comment 11.

In this section we show preliminary numerical results obtained with the DG method implemented in \thornado\ to solve the non-relativistic and special relativistic Euler equations.  
We use the ideal gas equation of state where the pressure $p$ is related to the internal energy density $e$ by $p=(\Gamma-1)e$, and where $\Gamma$ is the (constant) adiabatic index.  
Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$th coordinate direction, respectively.  
We use polynomials of degree $k=2$ combined with SSP-RK3 time stepping, and all the tests were run with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.  
We use the HLL Riemann solver when solving the non-relativistic Euler equations and the HLLC Riemann solver when solving the special relativistic Euler equations.  
The purpose of the tests is to gauge the performance of the DG implementation on a set of benchmarks as an initial measure of its suitability for future CCSN simulations.

@@

\subsubsection{Isentropic vortex}
This test from \cite{shu_1997} is included to verify the accuracy of the DG method implemented in \thornado.  
The periodic computational domain is given by $D=[-5,5]\times[-5,5]$.  
The initial density and pressure are given by $\rho_{0}=\big(\,1-\f{(\Gamma-1)\,\beta^{2}}{(8\pi\Gamma)}\exp\big(1-r^{2}\big)\,\big)^{1/(\Gamma-1)}$ and $P_{0}=\rho^{\Gamma}$, where $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}$, while the velocity components are $v_{0}^{1}=1-\f{x^{2}\beta}{2\pi}\,\exp\big((1-r^{2})/2\big)$ and $v_{0}^{2}=1+\f{x^{1}\beta}{2\pi}\,\exp\big((1-r^{2})/2\big)$.  
The strength of the vortex is set to $\beta=5$, and we use $\Gamma=1.4$.  
We evolve this test until $t=t_{f}=10$, when the vortex has returned to its initial position.

>>>>

In this section we show preliminary numerical results obtained with the DG method implemented in \thornado\ to solve the non-relativistic and special relativistic Euler equations.  
We use the ideal gas equation of state where the pressure $p$ is related to the internal energy density $e$ by $p=(\Gamma-1)e$, and where $\Gamma$ is the (constant) adiabatic index.  
Let the $d$-dimensional computational domain be $D=\times_{i=1}^{d}[\xMin^{i},\xMax^{i}]$, where $\xMin^{i}$ and $\xMax^{i}$ denote the coordinates of the inner and outer boundary in the $i$th coordinate direction, respectively.  
To limit the scope of this initial study, we use polynomials of degree $k=2$ (except in Section~\ref{sec:isentropicVortex}, where we also use $k=1$ and $k=3$) combined with SSP-RK3 time stepping, and run all the tests with a Courant-Friedrichs-Lewy (CFL) factor of $C=0.1$.  
We use the HLL Riemann solver when solving the non-relativistic Euler equations and the HLLC Riemann solver when solving the special relativistic Euler equations.  
The purpose of the tests is to gauge the performance of the DG implementation on a set of benchmarks as an initial measure of its suitability for future CCSN simulations.

@@

\subsubsection{Isentropic vortex}
\label{sec:isentropicVortex}

This test from \cite{shu_1997} is included to verify the accuracy of the DG method implemented in \thornado.  
The periodic computational domain is given by $D=[-5,5]\times[-5,5]$.  
The initial density and pressure are given by $\rho_{0}=\big(\,1-\f{(\Gamma-1)\,\beta^{2}}{(8\pi\Gamma)}\exp\big(1-r^{2}\big)\,\big)^{1/(\Gamma-1)}$ and $P_{0}=\rho^{\Gamma}$, where $r=\sqrt{(x^{1})^{2}+(x^{2})^{2}}$, while the velocity components are $v_{0}^{1}=1-\f{x^{2}\beta}{2\pi}\,\exp\big((1-r^{2})/2\big)$ and $v_{0}^{2}=1+\f{x^{1}\beta}{2\pi}\,\exp\big((1-r^{2})/2\big)$.  
The strength of the vortex is set to $\beta=5$, and we use $\Gamma=1.4$.  
We evolve this test until $t=t_{f}=10$, when the vortex has returned to its initial position.
